---
title: "Introduction to Binomial"
author: "Francesco Dalla Ricca"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(Binomial)
```

##Binomial Statistics

This package lets you run statistical analysis on binomial distribution and even make graphs to better visualize the data.

##Creating a binomial distribution

Use the bin_distribution() function to make a data frame with the probability of differing amounts of success.
```{r}
bindis <- bin_distribution(trials = 5, prob = 0.5)
bindis
```

If you want to see the data frame in the form of a plot:
```{r}
plot(bindis)
```

##Cumulative distribution

Cumulative distribution is like a binomial distribution except it also shows the cumulative odds of each amount of success:
```{r}
cumdis <- bin_cumulative(trials = 5, prob = 0.5)
cumdis
```

And to see the data frame in the form of a plot:
```{r}
plot(cumdis)
```

##The Choose function
In order to calculate the number of combinations of k successes in n trials, uses the bin_choose() function like so:

```{r}
bin_choose(n = 5, k = 2)
```

You can also run bin_choose on a vector of k successes to see the different possible combinations of different amounts of success in n trials

```{r}
bin_choose(n = 5, k = 1:3)
```

##The Probability function
To see the probability of getting k successes in n trials, use the bin_probability() function

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

Like bin_choose, you can also input a vector for the successeses
```{r}
bin_probability(success = 1:3, trials = 5, prob = 0.5)
```

##The Binvar function
The bin_variable() function returns a binomial random variable object
```{r}
bin_variable(trials = 10, prob = 0.5)
```
